Paper Figures and Text

### 2024-02-20 Fish Data Analysis/Paper_Figures.qmd
Fixing file size commits

light_no_ab_color = "#d4d7dd"
light_ab_color = "#f5ba9e"
dark_no_ab_color = "#5e94d4"
sim_color = "#777777"

@@

```{r}
annushka_turning_data <- read.csv("Data/Annushka_Turning_Data_Wall.csv") %>%
                           #filter(Next.to.Wall == 0) %>%
                           mutate(Flow = ifelse(Flow == "F0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation %in% c("LN","TN"), "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "DN", "Light", "Dark")) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           mutate(Fish_Num_Ratio = No..Fish.Right/8) %>%
                           mutate(Fish_Ratio = paste(No..Fish.Left,No..Fish.Right,sep=":")) %>%
                           filter(Fish_Ratio %in% c("7:0","6:1","5:2","4:3","3:4","2:5","1:6","0:7")) %>%
                           mutate(Fish_Ratio = fct_relevel(Fish_Ratio,
                                                           c("7:0","6:1","5:2","4:3",
                                                             "3:4","2:5","1:6","0:7"))) %>%
                           mutate(turn_bool = ifelse(Turn.Direction == "right",1,0)) %>% 
                           select(-c("Turn.Start.Frame","Turn.End.Frame","Fish","Appox.Turn.Angle","X","Next.to.Wall")) %>%
                           rename("Turn_Dir" = "Turn.Direction")  %>%
                           rename("Fish_Left" = "No..Fish.Left")  %>%
                           rename("Fish_Right" = "No..Fish.Right")  %>%
                           mutate(Type = "Eight Fish")

@@

all_turning_data <- rbind(annushka_turning_data,single_fish_turning_data)

@@

```{r}
eight_fish_still <- ggplot(turning_data_sum %>% filter(Type == "Eight Fish") %>% filter(Flow == "Still Water"),
       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point()+
  #geom_line(alpha = 0.25) +
  geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
  #facet_wrap(~ Darkness + Ablation) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  ylim(0,1) +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color)) +
  #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))+ 
  labs(color = "Sensory Conditions")+
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))

eight_fish_flow <- ggplot(turning_data_sum %>% filter(Type == "Eight Fish") %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point()+
  #geom_line(alpha = 0.25) +
  geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
  #facet_wrap(~ Darkness + Ablation) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  ylim(0,1) +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color)) +
  #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))+ 
  labs(color = "Sensory Conditions")+
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))

@@

placeholder_tibble <- tibble("Fish_Ratio" = c("0:7","0:7","3:4"),
                             "Fish_Num_Ratio" = c(0.875,0.875,0.5),
                             "Flow" = c("Still Water","Still Water","Still Water"),
                             "Ablation" = c("No Ablation","Ablated","Ablated"),
                             "Darkness" = c("Light","Light","Light"),
                             "Type" = c("Combined Single","Combined Single","Combined Single"),
                             "n" = c(0,0,0))

turning_data_sum <- turning_data_sum %>% ungroup()

turning_data_sum <- full_join(turning_data_sum,placeholder_tibble)

dark_eight_and_single_graph <- ggplot(turning_data_sum %>% filter(Flow == "Still Water" & Darkness == "Dark"),
       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = Type))+
  geom_point()+
  geom_col(aes(x = Fish_Num_Ratio, y = n/80, fill = Type), color = NA, alpha = 0.3, position = "dodge2")+
  geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  scale_colour_manual(values = c(sim_color,dark_no_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
  scale_fill_manual(values = c(sim_color,dark_no_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
  #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))+ 
  labs(color = "School Type")+
  theme(axis.text.x = element_text(size = text_size/2),
        axis.text.y = element_text(size = text_size/2),
        axis.title.y = element_text(size = text_size/2))+
  guides(fill = FALSE)+
  scale_y_continuous("Probability of a Right Turn",
                     sec.axis = sec_axis(~.*80, name = "Number of Datapoints"),
                     limits = c(0, 1))

ablation_eight_and_single_graph <- ggplot(turning_data_sum %>% filter(Flow == "Still Water" & Ablation == "Ablated"),
       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = Type))+
  geom_point()+
  geom_col(aes(x = Fish_Num_Ratio, y = n/80, fill = Type), color = NA, alpha = 0.3, position = "dodge2")+
  geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  ylim(0,1) +
  scale_colour_manual(values = c(sim_color,light_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
  scale_fill_manual(values = c(sim_color,light_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
  #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))+ 
  labs(color = "School Type")+
  theme(axis.text.x = element_text(size = text_size/2),
        axis.text.y = element_text(size = text_size/2),
        axis.title.y = element_text(size = text_size/2))+
  guides(fill = FALSE)+
  scale_y_continuous("Probability of a Right Turn",
                     sec.axis = sec_axis(~.*80, name = "Number of Datapoints"),
                     limits = c(0, 1))

light_eight_and_single_graph <- ggplot(turning_data_sum %>% filter(Flow == "Still Water" & Ablation == "No Ablation" & Darkness == "Light"),
       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = Type))+
  geom_point()+
  geom_col(aes(x = Fish_Num_Ratio, y = n/80, fill = Type, color = none), color = NA, alpha = 0.3, position = "dodge2")+
  geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylim(0,1) +
  scale_colour_manual(values = c(sim_color,light_no_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
  scale_fill_manual(values = c(sim_color,light_no_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
  #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))+ 
  labs(color = "School Type")+
  theme(axis.text.x = element_text(size = text_size/2),
        axis.text.y = element_text(size = text_size/2),
        axis.title.y = element_text(size = text_size/2))+
  guides(fill = FALSE)+
  scale_y_continuous("Probability of a Right Turn",
                     sec.axis = sec_axis(~.*80, name = "Number of Datapoints"),
                     limits = c(0, 1))

light_eight_and_single_graph
ablation_eight_and_single_graph
dark_eight_and_single_graph
```

@@

turning_single_test_plot <- ggarrange(
          light_eight_and_single_graph, ablation_eight_and_single_graph, dark_eight_and_single_graph,
          labels = c("A", "B", "C"),
          ncol = 2, nrow = 2)

@@

```{r}
my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"))

nnd_still <- ggplot(school_data %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = NND,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = NND_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=NND_Mean_Val-NND_SD_Val, ymax=NND_Mean_Val+NND_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Still Water") +
  xlab("") +
  ylab("School NND (BL)") +
  theme_light()+ 
  theme(legend.position = "none") +
  ylim(0,2)+
  stat_compare_means(comparisons = my_comparisons, label.y = c(1.75), label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

nnd_flow <- ggplot(school_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = NND,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = NND_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=NND_Mean_Val-NND_SD_Val, ymax=NND_Mean_Val+NND_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Flow (2 BL/s)") +
  xlab("") +
  ylab("School NND (BL)") +
  theme_light()+ 
  theme(legend.position = "none") +
  #ylim(0,2)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

@@

### Height Plot

height_still <- ggplot(school_data %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = School_Height,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = Height_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Height_Mean_Val-Height_SD_Val, ymax=Height_Mean_Val+Height_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Still Water") +
  xlab("") +
  ylab("NND (BL)") +
  theme_light()+ 
  theme(legend.position = "none") +
  #ylim(0,3)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

height_flow <- ggplot(school_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = School_Height,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = Height_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Height_Mean_Val-Height_SD_Val, ymax=Height_Mean_Val+Height_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Flow (2 BL/s)") +
  xlab("") +
  ylab("NND (BL)") +
  theme_light()+ 
  theme(legend.position = "none") +
  #ylim(0,3)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

height_still
height_flow

height_glm <- glm(School_Height ~ Ablation*Darkness*Flow, data = school_data)
Anova(height_glm)
emmeans(height_glm, specs = pairwise ~ Ablation:Darkness | Flow)
```

@@

### Area

```{r}
my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"))

>>>>

light_no_ab_color = "#d4d7dd"
light_ab_color = "#f5ba9e"
dark_no_ab_color = "#5e94d4"
dark_ab_color = "#1E4371"
sim_color = "#777777"

@@

abalated_dark_turning_data <- read.csv("Data/ablated_dark_data_turning.csv") %>%
                           mutate(Flow = ifelse(Flow == "0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation  == "N", "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "N", "Light", "Dark")) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           mutate(Fish_Num_Ratio = Fish_Right/8) %>%
                           mutate(Fish_Ratio = paste(Fish_Left,Fish_Right,sep=":")) %>%
                           filter(Fish_Ratio %in% c("7:0","6:1","5:2","4:3","3:4","2:5","1:6","0:7")) %>%
                           mutate(Fish_Ratio = fct_relevel(Fish_Ratio,
                                                           c("7:0","6:1","5:2","4:3",
                                                             "3:4","2:5","1:6","0:7"))) %>%
                           mutate(turn_bool = ifelse(Turn_Dir == 0,1,0)) %>% 
                           select(-c("Singles","Frame","Fish")) %>%
                           mutate(Type = "Eight Fish")

annushka_turning_data <- read.csv("Data/Annushka_Turning_Data_Wall.csv") %>%
                           #filter(Next.to.Wall == 0) %>%
                           mutate(Flow = ifelse(Flow == "F0", "Still Water", "Flowing Water (2 BL/s)")) %>%
                           mutate(Ablation = ifelse(Ablation %in% c("LN","TN"), "No Ablation", "Ablated")) %>%
                           mutate(Darkness = ifelse(Darkness == "DN", "Light", "Dark")) %>%
                           mutate(Flow = factor(Flow), Ablation = factor(Ablation), Darkness = factor(Darkness)) %>%
                           mutate(Flow = fct_relevel(Flow, c("Still Water","Flowing Water (2 BL/s)"))) %>%
                           mutate(Ablation = fct_relevel(Ablation, c("No Ablation","Ablated"))) %>%
                           mutate(Darkness = fct_relevel(Darkness, c("Light","Dark"))) %>%
                           mutate(Flow_Ablation_Darkness = factor(paste(Flow,Ablation,Darkness,sep=", "))) %>%
                           mutate(Fish_Num_Ratio = No..Fish.Right/8) %>%
                           mutate(Fish_Ratio = paste(No..Fish.Left,No..Fish.Right,sep=":")) %>%
                           filter(Fish_Ratio %in% c("7:0","6:1","5:2","4:3","3:4","2:5","1:6","0:7")) %>%
                           mutate(Fish_Ratio = fct_relevel(Fish_Ratio,
                                                           c("7:0","6:1","5:2","4:3",
                                                             "3:4","2:5","1:6","0:7"))) %>%
                           mutate(turn_bool = ifelse(Turn.Direction == "right",1,0)) %>% 
                           select(-c("Turn.Start.Frame","Turn.End.Frame","Fish","Appox.Turn.Angle","X","Next.to.Wall")) %>%
                           rename("Turn_Dir" = "Turn.Direction")  %>%
                           rename("Fish_Left" = "No..Fish.Left")  %>%
                           rename("Fish_Right" = "No..Fish.Right")  %>%
                           mutate(Type = "Eight Fish")

@@

eight_fish_turning_data <- rbind(annushka_turning_data,abalated_dark_turning_data)

all_turning_data <- rbind(eight_fish_turning_data,single_fish_turning_data)

eight_fish_data_sum  <- eight_fish_turning_data %>% na.omit %>%
                                     group_by(Fish_Ratio,Fish_Num_Ratio,Flow,Ablation,Darkness,Flow_Ablation_Darkness,Type) %>%
                                     summarize(mean_right_turn = mean(turn_bool),
                                               sd_right_turn = sd(turn_bool),
                                               se_right_turn = sd_right_turn/sqrt(n()),
                                               n = n()) %>%
                                     ungroup()

single_fish_data_sum  <- single_fish_turning_data %>% na.omit %>%
                                     group_by(Fish_Ratio,Fish_Num_Ratio,Flow,Ablation,Darkness,Flow_Ablation_Darkness,Type) %>%
                                     summarize(mean_right_turn = mean(turn_bool),
                                               sd_right_turn = sd(turn_bool),
                                               se_right_turn = sd_right_turn/sqrt(n()),
                                               n = n()) %>%
                                     ungroup() %>%
                                     filter(Flow == "Still Water" & Darkness == "Light" & Ablation == "No Ablation")

@@

```{r}
eight_fish_still <- ggplot(turning_data_sum %>% filter(Type == "Eight Fish") %>% filter(Flow == "Still Water"),
       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point()+
  #geom_line(alpha = 0.25) +
  geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
  #facet_wrap(~ Darkness + Ablation) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  ylim(0,1) +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
  #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))+ 
  labs(color = "Sensory Conditions")+
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))

eight_fish_flow <- ggplot(turning_data_sum %>% filter(Type == "Eight Fish") %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point()+
  #geom_line(alpha = 0.25) +
  geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
  #facet_wrap(~ Darkness + Ablation) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  ylim(0,1) +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color,dark_ab_color)) +
  #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))+ 
  labs(color = "Sensory Conditions")+
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))

@@

```{r}
placeholder_tibble <- tibble("Fish_Ratio" = c("0:7"),
                             "Fish_Num_Ratio" = c(0.875),
                             "Flow" = c("Still Water"),
                             "Ablation" = c("No Ablation"),
                             "Darkness" = c("Light"),
                             "Type" = c("Combined Single"),
                             "n" = c(0))

light_no_ab_eight_single_graph_data <- eight_fish_data_sum %>% 
                                      filter(Flow == "Still Water" & Darkness == "Light" & Ablation == "No Ablation") %>%
                                      full_join(.,single_fish_data_sum) %>%
                                      full_join(.,placeholder_tibble)

light_ab_eight_single_graph_data <- eight_fish_data_sum %>% 
                                      filter(Flow == "Still Water" & Darkness == "Light" & Ablation == "Ablated") %>%
                                      full_join(.,single_fish_data_sum) %>%
                                      full_join(.,placeholder_tibble)

dark_no_ab_eight_single_graph_data <- eight_fish_data_sum %>% 
                                      filter(Flow == "Still Water" & Darkness == "Dark" & Ablation == "No Ablation") %>%
                                      full_join(.,single_fish_data_sum) %>%
                                      full_join(.,placeholder_tibble)

dark_ab_eight_single_graph_data <- eight_fish_data_sum %>% 
                                      filter(Flow == "Still Water" & Darkness == "Dark" & Ablation == "Ablated") %>%
                                      full_join(.,single_fish_data_sum) %>%
                                      full_join(.,placeholder_tibble)

light_eight_and_single_graph <- ggplot(light_no_ab_eight_single_graph_data,
       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = Type))+
  geom_point()+
  geom_col(aes(x = Fish_Num_Ratio, y = n/80, fill = Type, color = none), color = NA, alpha = 0.3, position = "dodge2")+
  geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylim(0,1) +
  scale_colour_manual(values = c(sim_color,light_no_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
  scale_fill_manual(values = c(sim_color,light_no_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
  #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))+ 
  labs(color = "School Type")+
  theme(axis.text.x = element_text(size = text_size/2),
        axis.text.y = element_text(size = text_size/2),
        axis.title.y = element_text(size = text_size/2))+
  guides(fill = FALSE)+
  scale_y_continuous("Probability of a Right Turn",
                     sec.axis = sec_axis(~.*80, name = "Number of Datapoints"),
                     limits = c(0, 1))

ablation_eight_and_single_graph <- ggplot(light_ab_eight_single_graph_data,
       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = Type))+
  geom_point()+
  geom_col(aes(x = Fish_Num_Ratio, y = n/80, fill = Type), color = NA, alpha = 0.3, position = "dodge2")+
  geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  ylim(0,1) +
  scale_colour_manual(values = c(sim_color,light_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
  scale_fill_manual(values = c(sim_color,light_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
  #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))+ 
  labs(color = "School Type")+
  theme(axis.text.x = element_text(size = text_size/2),
        axis.text.y = element_text(size = text_size/2),
        axis.title.y = element_text(size = text_size/2))+
  guides(fill = FALSE)+
  scale_y_continuous("Probability of a Right Turn",
                     sec.axis = sec_axis(~.*80, name = "Number of Datapoints"),
                     limits = c(0, 1))

dark_eight_and_single_graph <- ggplot(dark_no_ab_eight_single_graph_data,
       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = Type))+
  geom_point()+
  geom_col(aes(x = Fish_Num_Ratio, y = n/80, fill = Type), color = NA, alpha = 0.3, position = "dodge2")+
  geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  scale_colour_manual(values = c(sim_color,dark_no_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
  scale_fill_manual(values = c(sim_color,dark_no_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
  #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))+ 
  labs(color = "School Type")+
  theme(axis.text.x = element_text(size = text_size/2),
        axis.text.y = element_text(size = text_size/2),
        axis.title.y = element_text(size = text_size/2))+
  guides(fill = FALSE)+
  scale_y_continuous("Probability of a Right Turn",
                     sec.axis = sec_axis(~.*80, name = "Number of Datapoints"),
                     limits = c(0, 1))

dark_ablation_eight_and_single_graph <- ggplot(dark_ab_eight_single_graph_data,
       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = Type))+
  geom_point()+
  geom_col(aes(x = Fish_Num_Ratio, y = n/80, fill = Type), color = NA, alpha = 0.3, position = "dodge2")+
  geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  scale_colour_manual(values = c(sim_color,dark_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
  scale_fill_manual(values = c(sim_color,dark_ab_color), labels=function(x){sub("\\s", "\n", x)}) +
  #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))+ 
  labs(color = "School Type")+
  theme(axis.text.x = element_text(size = text_size/2),
        axis.text.y = element_text(size = text_size/2),
        axis.title.y = element_text(size = text_size/2))+
  guides(fill = FALSE)+
  scale_y_continuous("Probability of a Right Turn",
                     sec.axis = sec_axis(~.*80, name = "Number of Datapoints"),
                     limits = c(0, 1))

light_eight_and_single_graph
ablation_eight_and_single_graph
dark_eight_and_single_graph
dark_ablation_eight_and_single_graph
```

@@

turning_single_test_plot <- ggarrange(
          light_eight_and_single_graph, ablation_eight_and_single_graph, 
          dark_eight_and_single_graph, dark_ablation_eight_and_single_graph,
          labels = c("A", "B", "C", "D"),
          ncol = 2, nrow = 2)

@@

my_comparisons <- list(c("No Ablation, Light", "No Ablation, Dark"),
                       c("No Ablation, Light", "Ablated, Dark"), 
                       c("Ablated, Light", "No Ablation, Dark"),
                       c("Ablated, Light", "Ablated, Dark"))

nnd_still <- ggplot(school_data %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = NND,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = NND_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=NND_Mean_Val-NND_SD_Val, ymax=NND_Mean_Val+NND_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Still Water") +
  xlab("") +
  ylab("School NND (BL)") +
  theme_light()+ 
  theme(legend.position = "none") +
  ylim(0,2.5)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

my_comparisons <- list(c("No Ablation, Light", "Ablated, Dark"), c("Ablated, Light", "Ablated, Dark"))

nnd_flow <- ggplot(school_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = NND,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = NND_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=NND_Mean_Val-NND_SD_Val, ymax=NND_Mean_Val+NND_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color, dark_ab_color)) +
  #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Flow (2 BL/s)") +
  xlab("") +
  ylab("School NND (BL)") +
  theme_light()+ 
  theme(legend.position = "none") +
  ylim(0,2.5)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = text_size),
        axis.text.y = element_text(size = text_size),
        axis.title.y = element_text(size = text_size))+
  scale_x_discrete(labels=function(x){sub(",\\s", "\n", x)})

@@

@@
